Decentralized autonomous organization to automate governance\\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2016-04-07 paper/Paper.tex
update debating period

A problem this simple fix doesn't address is voter apathy: some token holders might not be actively involved in the DAO and might not follow proposals closely. An attacker could use this to their advantage. Even though the minority has the chance to retrieve their funds and split the DAO, some could be unaware of the situation and fail to act. For the DAO to be considered safe, it is required that inactive token holders must also be protected from losing their tokens. Our proposed solution is implemented by limiting each individual DAO to a single service provider. This service provider controls the only account that can receive ether from the DAO, across all proposals. In addition, the service provider can build a “whitelist” of addresses that the DAO is allowed to send funds to. This gives the service provider of the DAO considerable power. To prevent the abuse of this power, it is possible for the DAO to vote for a new service provider, which may result in a split of the DAO as described above.

@@

The process of choosing a new service provider is as follows:
Any token holder can submit a proposal for a new service provider. In this case, no proposal deposit is required, because an attacker could vote for an extremely high deposit, preventing any splits. The debating period for this proposal is $10$ days.
This is $4$ days less than the minimum required for regular proposals, allowing anyone to retrieve their funds before a potentially malicious proposal goes through. There is no quorum requirement, so that every token holder has the ability to split into their own DAO. 
The debating period is used to discuss (on or off-chain) the new service provider and conduct a first vote that's non-binding. After this first vote, token holders can cast a second one to confirm its results. In the case a majority opts to  keep the original service provider, the minority can either change their vote to keep the original service provider in order to avoid a split, or inversely they can confirm their vote for a new service provider and move their portion of the funds to a new DAO.

>>>>

A problem this simple fix doesn't address is voter apathy: some token holders might not be actively involved in the DAO and might not follow proposals closely. An attacker could use this to their advantage. Even though the minority has the chance to retrieve their funds and split the DAO, some could be unaware of the situation and fail to act. For the DAO to be considered safe, it is required that inactive token holders must also be protected from losing their ether. Our proposed solution is implemented by limiting each individual DAO to a single service provider. This service provider controls the only account that can receive ether from the DAO, across all proposals. In addition, the service provider can build a “whitelist” of addresses that the DAO is allowed to send funds to. This gives the service provider of the DAO considerable power. To prevent the abuse of this power, it is possible for the DAO to vote for a new service provider, which may result in a split of the DAO as described above.

@@

The process of choosing a new service provider is as follows:
Any token holder can submit a proposal for a new service provider. In this case, no proposal deposit is required, because an attacker could vote for an extremely high deposit, preventing any splits. The debating period for this proposal is $7$ days.
This is $7$ days less than the minimum required for regular proposals, allowing anyone to retrieve their funds before a potentially malicious proposal goes through. There is no quorum requirement, so that every token holder has the ability to split into their own DAO. 
The debating period is used to discuss (on or off-chain) the new service provider and conduct a first vote that's non-binding. After this first vote, token holders can cast a second one to confirm its results. In the case a majority opts to  keep the original service provider, the minority can either change their vote to keep the original service provider in order to avoid a split, or inversely they can confirm their vote for a new service provider and move their portion of the funds to a new DAO.
